---
title: "AdvancedR_ch2"
author: "Hannah Kim"
date: "2024-06-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 2.1.3
### 1

There are logical, integer, double(numeric), character, complex and raw atomic
vectors.
The atomic vectors are different from the lists because the elements of the lists
can be of any type, including lists.

### 2
`is.vector()` and `is.numeric()` both do not test if an object is a vector(or numeric vector).
They both return `TRUE` only if the object is a vector with no attributes
or a number (both integer and double vectors).

### 3
```{r}
# 1 0
c(1, FALSE)

# "a" "1"
c("a", 1)

# Returns the list that has: a list that has 1 as component, and another list that has "a" as component
c(list(1), "a")

# 1 1 (1 and 1L difference?)
c(TRUE, 1L)
c(1L, TRUE)
```

### 4
If the elements of a list have different types, `as.vector()` would not work; 
instead, `unlist()` uses the same coercion rules as `c()` to convert a list to an atomic vector.

### 5
1 =="1" is true due to type coercion. 
When comparing a numeric value (1) and a character value ("1"), R automatically coerces
the character to a numeric value if possible. 
Thus, "1" is coerced to 1, and 1 == 1 is true.
-1 < FALSE is true because in R, logical values can be coerced to integers 
where `FALSE` becomes 0 and `TRUE` becomes 1.
Therefore, the comparison -1 < `FALSE` is equivalent to -1 < 0, which is true.
"one" < 2 is false because when comparing a character value ("one") with a numeric value (2),
R does not coerce the character to a numeric value because "one" cannot be interpreted as a number.

### 6
The default `NA` in R is a logical vector of length 1 because logical is the simplest type
in R's type hierarchy.
Logical vectors are special because they can be coerced into other types
(integer, double, character) seamlessly.
For instance, `TRUE` becomes 1 and `FALSE` becomes 0 when coerced to numeric types.

## Exercise 2.2.2
### 1
The attribute is not missing; it is there but not displayed because
the comment attribute is not one of the core attributes that print displays by default.
The print function in R does not display attributes other than names, dimensions, and class by default.

### 2
When you modify the levels of a factor, the internal integer representation of the factor
remains the same, but the corresponding level labels are updated to the new values you assign.
Here, the levels of f1 are reversed; that is, the first level becomes the last,
the second level becomes the second last, and so on.

### 3
```{r}
f2 <- rev(factor(letters))
```

This code reverses the factor levels and then applies the rev function to the factor.
This means that the factor f2 will have the reversed order of the levels of f1,
but the factor levels themselves are not reversed, just the ordering of the factor elements.

```{r}
f3 <- factor(letters, levels = rev(letters))
```

This code creates a factor with the levels explicitly set to the reversed order of letters.
This means that the factor f3 will have the elements in the same order as f1,
but the levels will be reversed.

## Exercise 2.3.1
### 1
When dim() is applied to a vector, it returns `NULL`. 

### 2
If `is.matrix(x)` is `TRUE`, then `is.array(x)` will also return `TRUE`.
In R, a matrix is a special case of an array with two dimensions.
Therefore, any object that is a matrix is also an array, but not all arrays are matrices.

### 3
```{r}
x1 <- array(1:5, c(1, 1, 5))
x2 <- array(1:5, c(1, 5, 1))
x3 <- array(1:5, c(5, 1, 1))
```

`x1` is a 3-dimensional array with dimensions 1x1x5.
It represents a single row with 5 columns in a 3-dimensional space.
`x2` is a 3-dimensional array with dimensions 1x5x1.
It represents a single column with 5 rows in a 3-dimensional space. 
`x3` is a 3-dimensional array with dimensions 5x1x1.
It represents a 5-element vector but arranged as a 3-dimensional array.

## Exercise 2.4.5
### 1
A data frame in R possesses several attributes including: `names()`,
which is a character vector giving the names of the columns, `colnames()`,
providing the same column names, and `rownames()`, a character vector giving the names of the rows.
Additionally, a data frame has a `class` attribute always set to `"data.frame"`, 
indicating its type, and a `dim` attribute representing the dimensions of the data frame,
i.e., the number of rows and columns.

### 2
When as.matrix() is applied to a data frame with columns of different types,
it coerces all the columns to the same type, usually to the most general type 
that can accommodate all the data.
If a data frame has numeric and character columns, the numeric data will be coerced to
character to maintain a consistent type across the entire matrix.
This is because matrices can only hold elements of the same type,
unlike data frames that can hold elements of different types in different columns.

### 3
Yes, you can have a data frame with 0 rows and/or 0 columns.